---
title: "Habitat Suitability Analysis of Bijaya Sal"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    number_sections: yes
number_sections: yes
geometry: left = 2.5cm, right = 2cm, top = 2cm, bottom = 2cm
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{sectsty}
- \usepackage{paralist}
- \usepackage{setspace}\spacing{1.5}
- \usepackage{fancyhdr}
- \usepackage{lastpage}
- \usepackage{dcolumn}
- \usepackage{natbib}\bibliographystyle{agsm}
- \usepackage[nottoc, numbib]{tocbibind}
---

\pagenumbering{arabic}

\pagenumbering{gobble}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\pagebreak

\tableofcontents

\newpage

\pagenumbering{arabic}

# Load Packages

```{r message=FALSE, warning=FALSE, , echo=T}

library(sf) # Load raster and Vector data
library(mapview) # Visualization of Vector Data
library(raster) # Load raster and Vector data
library(spThin) #To thin the spatial data
```

# Load Presence data of Bijaya Sal ( *Pterocarpus marsupium* )

The coordinate of present data is in WGS 84 UTM 44 system.

```{r , echo=FALSE}
bijaysal<-read.csv("~/00_work/00_bijaysal/data/bijasal_presence.csv",header=T)
names(bijaysal)
```

# Split of Data into Training and Test Set

The data is splited into Training and Test set. The 80% of the total data is used for training the model and rest data set is used for evaluate the model.


```{r}


```
