---
title: "Habitat Suitability Analysis of Bijaya Sal"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    number_sections: yes
number_sections: yes
geometry: left = 2.5cm, right = 2cm, top = 2cm, bottom = 2cm
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{sectsty}
- \usepackage{paralist}
- \usepackage{setspace}\spacing{1.5}
- \usepackage{fancyhdr}
- \usepackage{lastpage}
- \usepackage{dcolumn}
- \usepackage{natbib}\bibliographystyle{agsm}
- \usepackage[nottoc, numbib]{tocbibind}
---

\pagenumbering{arabic}

\pagenumbering{gobble}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\pagebreak

\tableofcontents

\newpage

\pagenumbering{arabic}

# Load Packages

```{r message=FALSE, warning=FALSE, , echo=T}

library(sf) # Load raster and Vector data
library(mapview) # Visualization of Vector Data
library(raster) # Load raster and Vector data
library(spThin) #To thin the spatial data
library(usdm) # VIF (variance Inflation Factor)measures the severity of multicollinearity in regression analysis. 
library(predicts)
library(RColorBrewer)

```

# Load Presence data of Bijaya Sal ( *Pterocarpus marsupium* )

The coordinate of present data is in WGS 84 UTM 44 system.

```{r , echo=FALSE}
bijaysal<-read.csv("~/00_work/00_bijaysal/data/bijasal_presence.csv",header=T)
names(bijaysal)
```

# Split of Data into Training and Test Set

The data is splited into Training and Test set. The 70% of the total data is used for training the model and rest data set is used for evaluate the model.


```{r}
#make this example reproducible
set.seed(1)
#use 70% of dataset as training set and 30% as test set
sample <- sample(c(TRUE, FALSE), nrow(bijaysal), replace=TRUE, prob=c(0.7,0.3))
train  <- bijaysal[sample, ]
test   <- bijaysal[!sample, ]

```

## Train data 

```{r}
train_sf<-st_as_sf(train, coords = c("easting", "northing"), crs = 32644)
train_wgs<-st_transform(train_sf,crs=4326)
train_sp<-as_Spatial(train_wgs)
train_data<-data.frame(train_sp)
names(train_data)
names(train_data)[3]<- "lon"
names(train_data)[4]<- "lat"
train_data$species<-"bijayasal"
```

### Spatial thining of Train data

Here we are going to keep only the train point which is 1 km far.

```{r message=FALSE, warning=FALSE}

#thinning the points
# thinned_data <- thin(
#   loc.data = train_data, 
#   lat.col = "lat", #latitude, the string name should be modified accordingly
#   long.col = "lon", #longitude, the string name should be modified accordingly
#   spec.col = "species", #name of the column with species name
#   thin.par = 1, #distance of the thinned points
#   reps = 1, #number of repetition, for randomness
#   locs.thinned.list.return = TRUE, #If true, the ‘list‘ of the data.frame of thinned locs resulting from each replication is returned 
#   write.files = T, #whether to create the csv file or not
#   max.files = 10, #number of csv files created.
#   out.dir = "./data", #output directory in which the folder is created
#   out.base = "train", #the name of folders thus created
#   write.log.file = F, #whether to create log file or nor 
#   log.file = "noct.txt" # create/append log file of thinning run
# )

train_pts<-read.csv("data/train_thin1.csv",header=T)
trainsf<-st_as_sf(train_pts, coords = c("lon", "lat"), crs = 4326)
#write_sf(trainsf,"./data/train_thined.shp")

```

## Test data 

```{r}
test_sf<-st_as_sf(test, coords = c("easting", "northing"), crs = 32644)
test_wgs<-st_transform(test_sf,crs=4326)
test_sp<-as_Spatial(test_wgs)
test_data<-data.frame(test_sp)
names(test_data)
names(test_data)[3]<- "lon"
names(test_data)[4]<- "lat"
test_data$species<-"bijayasal"
```

### Spatial thining of Test data

Here we are going to keep only the test point which is 1 km far.

```{r message=FALSE, warning=FALSE}

#thinning the points
# thinned_data <- thin(
#   loc.data = test_data, 
#   lat.col = "lat", #latitude, the string name should be modified accordingly
#   long.col = "lon", #longitude, the string name should be modified accordingly
#   spec.col = "species", #name of the column with species name
#   thin.par = 1, #distance of the thinned points
#   reps = 1, #number of repetition, for randomness
#   locs.thinned.list.return = TRUE, #If true, the ‘list‘ of the data.frame of thinned locs resulting from each replication is returned 
#   write.files = T, #whether to create the csv file or not
#   max.files = 10, #number of csv files created.
#   out.dir = "./data", #output directory in which the folder is created
#   out.base = "test", #the name of folders thus created
#   write.log.file = F, #whether to create log file or nor 
#   log.file = "noct.txt" # create/append log file of thinning run
# )
test_pts<-read.csv("data/test_thin1.csv",header=T)
testsf<-st_as_sf(test_pts, coords = c("lon", "lat"), crs = 4326)
#write_sf(testsf,"./data/test_thined.shp")
```

# Loading Worldclim data and Topographic data

#BIO1 = Annual Mean Temperature
#BIO2 = Mean Diurnal Range (Mean of monthly (max temp - min temp))
#BIO3 = Isothermality (BIO2/BIO7) (* 100)
#BIO4 = Temperature Seasonality (standard deviation *100)
#BIO5 = Max Temperature of Warmest Month
#BIO6 = Min Temperature of Coldest Month
#BIO7 = Temperature Annual Range (BIO5-BIO6)
#BIO8 = Mean Temperature of Wettest Quarter
#BIO9 = Mean Temperature of Driest Quarter
#BIO10 = Mean Temperature of Warmest Quarter
#BIO11 = Mean Temperature of Coldest Quarter
#BIO12 = Annual Precipitation
#BIO13 = Precipitation of Wettest Month
#BIO14 = Precipitation of Driest Month
#BIO15 = Precipitation Seasonality (Coefficient of Variation)
#BIO16 = Precipitation of Wettest Quarter
#BIO17 = Precipitation of Driest Quarter
#BIO18 = Precipitation of Warmest Quarter
#BIO19 = Precipitation of Coldest Quarter


```{r}
ls.dir<-"./data/wc2.1_30s_bio/"
rlst <- list.files(ls.dir, pattern = "*.tif$",full.names = T)
worldclim<-rast(rlst)
names(worldclim)
projection(worldclim)
####Load DEM data ####
elevation<-rast("./data/nepal_dem90m.tif")
elev<-resample(elevation,worldclim, method="bilinear")
#slope and Aspect from DEM
slope<- terrain(elev, "slope", unit= "degrees", neighbors=8)
aspect <- terrain(elev, "aspect",unit= "degrees", neighbors=8) 
imag_com<-c(worldclim,elev,slope,aspect)
names(imag_com)
class(imag_com)
#terra::writeRaster(imag_com,"./data/imag_com.tif",overwrite=TRUE)
```
# Multicolinearity Check
VIF ()

